A Framework for Classification of Social Machines

### 2013-02-15 latex/sig-alternate.tex
Added particapatory constructs

\begin{enumerate}
\item Roles emerging in the social machine.
   \indent In addition to designed and implemented roles such as {\it moderator} and {\it administrator}, emerging roles include motivations of the participant, such as {\it trolls}, {\it spammers}, {\it domain experts}, {\it social nexus}, and {\it re-blogger}.
\item Quality of contributions
    \indent For any social machine, the quality of contributions will vary. While some
    issues with quality can be predicted and protected against (e.g., through 
    multi-user result agreement on Mechanical Turk~\cite{ipeirotis2010quality}), some
    particular issues with quality cannot always be predicted ahead of time.
\item Content of contributions
    \indent While a system operator may design their social machine to generate specific
    types of content, participants may subvert the system in order to generate other types,
    or to concentrate on areas that were unforeseen at the time of launch, but are now seen
    as useful to the operators.
\item Global / cultural reach
    \indent 
\item Task reach --- what do people use it for?
\item Active/Passive participation roles 
\end{enumerate}

>>>>

\begin{enumerate}
\item {\bf Roles emerging in the social machine}
   \newline In addition to designed and implemented roles such as {\it moderator} and {\it administrator}, emerging roles include motivations of the participant, such as {\it trolls}, {\it spammers}, {\it domain experts}, {\it social nexus}, and {\it re-blogger}.
\item {\bf Quality of contributions}
    \newline For any social machine, the quality of contributions will vary. While some
    issues with quality can be predicted and protected against (e.g., through 
    multi-user result agreement on Mechanical Turk~\cite{ipeirotis2010quality}), some
    particular issues with quality cannot always be predicted ahead of time.
\item {\bf Content of contributions}
    \newline While a system operator may design their social machine to generate specific
    types of content, participants may subvert the system in order to generate other types,
    or to concentrate on areas that were unforeseen at the time of launch, but are now seen
    as useful to the operators. It is also possible that multiple social machines can be
    combined/linked by users to further expand the types of contributions they produce.
\item {\bf Global / cultural reach}
    \newline A social machine may naturally focus on a narrow geographic area, for example
    an Ushahidi-based social machine for local elections~\cite{meier2008crisis} or
    natural disasters~\cite{morrow2011independent}. Such machines are unlikely to be
    re-purposed by participants outside of that area. However, some machines have been
    created for a single cultural/global area, but have potential global relevance that was
    unforeseen early on. An example is the fall-off of English-language users of the
    social network ``Orkut,'' which gained significant usage elsewhere, particularly in
    Brazil.
\item {\bf Task reach --- what do people use it for?}
    \newline In addition to breaking cultural barriers, user have also shown that they can
    use social machines for tasks that were not set up by the system operators. For example
    the identification of ``Green Pea Galaxies'' using the GalaxyZoo social machine for
    astronomy~\cite{greenpea}. Users were not originally asked to identify these types, but
    a number of users identified them, and the software was modified to include them,
    resulting in their discovery as a new type of galaxy.
\item {\bf Active/Passive participation roles}
    \newline When it comes to participation in social machines, there are levels of
    participation that can be classified as being ``active'' and being ``passive.'' These
    roles may not be particularly designed into systems, but may be exhibited over time.
    Particularly noteworthy examples can be seen in news and link aggregation social
    machines such as Reddit and Digg, where users can both submit links and vote on links.
    The frequency of each of these activities can vary wildly, with a small
    minority of users controlling the links that rise to the top~\cite{digg}.
\end{enumerate}
